\documentclass[11pt]{article}

\input{preamble.tex}

% document starts here
\begin{document}
\parskip=\bigskipamount
\parindent=0.0in
\thispagestyle{empty}
\input{header.tex}

\bigskip\bigskip
\centerline{\Large \bf ECON-GA-4005:  Project Guide}
\centerline{Revised: \today}

\section*{Overview}

One key outcome of this course is for you to produce a piece of work you can use
to demonstrate your computational skills to potential employers. That work will
come in the form of a Jupyter notebook. As you know, these notebooks allow you
to combine code, text, and graphics in one user-friendly document. We will add
them to our GitHub repository (with your permission) so that you can use a link
to show others what you've done. You will also be able to see what your
classmates have done.

The relatively loose structure in self-directed projects like this makes them
more challenging than most things you do in school. We think that also makes
them more interesting. They give you a chance to indulge your curiosity and show
off your creativity.

We have divided the project into components to keep you on track. The intent is
to make the project easier by breaking it down into a number of small,
manageable sub-projects. The early steps are graded only on whether you do them:
you get full points if you do them, none if you don't. We start with individual
work.  Partway along, we encourage you to form groups of two or three, but if
you'd prefer to do this on your own, that's ok, too.


\section*{Project outline}

The components of the project are
%
\begin{center}
      \begin{tabular}{lllrr}
            \toprule
            Assignment          & Format                           & Individual/Group & Points & Due    \\
            \midrule
            Three Project Ideas & Electronic (quiz on brightspace) & Individual       & 0      & Apr 7  \\
            Project Proposal    & Written (professional)           & Group            & 5      & Apr 23 \\
            Data Report         & Written (professional)           & Group            & 10     & May 7  \\
            Final Project       & Jupyter notebook                 & Group            & 85     & May 21 \\
            \bottomrule
      \end{tabular}
\end{center}

{\bf Dates are firm and not open for negotiation.}

Each part of the project must be uploaded to Brightspace before the deadline.


The components consist of:
\begin{itemize}

      \item {\bf Three project ideas.}

            Write down three project ideas. One or two sentences each is enough.
            Use your imagination.  Be creative.  Speak to others. Write down
            things that interest you. This will not be graded, but it will give
            you something to work with later on.

            Over the coming weeks, we recommend you keep your ears open for
            possible {\bf project ideas} --- and {\bf data sources\/}.

            \item{\bf Project proposal.}

            Form a group of between one and three --- no more --- and choose a
            single project from those you submitted --- or perhaps some other idea
            if you get a sudden flash of inspiration. Flesh out the project in more
            detail, {\bf including the data source, ideas for a model\/} and two
            figures you plan to produce. Total length should be no more than
            two pages.

            On the off-chance you missed the point:  you should {\bf be clear
                        about the data and type of model you plan to use\/}. If
            you can't get the data, your whole project can be
            derailed.

                  {\bf Did we mention data? Or models?}

      \item {\bf Data and Model report.}

            Describe your data and how you accessed it in enough detail that someone else
            could do it. Yes, that's ``accessed,'' past tense.  You should have done this
            already to make sure you have it. Include your Python code.

            Internet sources are preferred, because it allows others to use your code and
            follow up on your work.

            Also include notes about the type of model you plan to fit. You to
            not necessarily need to have fit the model at this stage, but you
            should show us what you are thinking. Now that you have the data,
            being explicit and clear (through writing) about how you plan to use
            the data is extremely helpful in spotting potential roadblocks and
            making sure you have a coherent plan.

      \item {\bf Final project.}

            You should submit your {\bf notebook\/} to Brightspace by the due date
            listed above. The submission should include any data or supplementary files
            needed to execute your project. The final writeup should be a Jupyter
            notebook and the file name should be your last names separated by dashes and
            a short title --- something like {\tt Jones-Smith-Zhang.ipynb}.

            Your project should include:
            \begin{itemize}
                  \item Description cell.  Put a Markdown cell at the top of your notebook that
                        includes the title of your project, a list of authors, and a short summary of
                        what you do.  Think of the last one as an advertisement to potential readers.
                  \item Data.  Description of data sources and the code to read the data into
                        Python and reformat it as needed. This should be done in enough detail that
                        someone else can reproduce what you've done.
                  \item Model.  Description of the model(s) used to analyze the data and
                        the code to fit the model. This should be done in enough detail
                        that someone else can reproduce what you've done.
                  \item Graphics.  A series of figures that tell us something interesting. Three
                        or four would be enough, but do what you think works best for your project.
                        Think about the narrative:  What story do you want to tell?
                  \item Conclusion. What was the main outcome or result of your project?
                        What did you learn? What should readers take away? Were you surprised
                        by anything? Is there futher work you or someone else could to do
                        extend your analysis?
            \end{itemize}

\end{itemize}


\section*{Free advice}

Some things to keep in mind:
%
\begin{itemize}
      \item {\bf Keep it simple.}

            Most project ideas turn out to be too big.  You're generally well-advised to
            carve out a manageable subset of what you think you can do. There's no reason to
            worry about this at the idea generation stage, but as you develop your project
            you may find that you need to focus more narrowly on a part of it.

      \item {\bf Find data.}  Make sure you can get the data you need. One way to
            assure this is to start with data and ask what you can do with it. Ideally you
            want the intersection (picture a Venn diagram) of an interesting idea and good
            data.  You can start with either one, but ideas are often easier to find than
            data. Or start with an existing project that uses data you can access yourself
            and extend it in some way.


      \item {\bf Ask for help.}
            We have years of experience with this kind of thing. If you're stuck, let us
            know and we'll try to help. You can also post questions on the class discussion
            board.

\end{itemize}


\section*{Grading}

Projects will be graded on their overall quality.  This includes, but is not
restricted to, these categories:
%
\begin{itemize}
      \item Quality of the idea.  Is the question clearly articulated?  Is it
            interesting? Does it have general appeal?
      \item Quality of the data.  Does the data support the idea? Is it the best data
            for this question?
      \item Quality of the model.  Did you choose an appropriate model for your data
            and question? Where you able to fit the model effectively?
      \item Degree of difficulty.  Some ideas are harder than others to implement. As
            in Olympic diving, you get credit for taking on a challenge.
      \item Professional look.  Does your project look professional?  Are the graphs
            easy to understand?  Are they clearly labeled?
      \item Demonstration of skills. Does your project showcase what you've learned in
            this class? Do you use some of the theory or algorithms we've worked on? How
            does your application of these tools impact your final writeup?
\end{itemize}


\input{footer.tex}


%\end{document}
\pagebreak
\thispagestyle{empty}
\input{header.tex}

\bigskip\bigskip
\centerline{\Large \bf CAP-6318:  Project Grade Sheet}
\centerline{Revised: \today}


\section*{Overall}

\begin{itemize} %\itemsep=0.75\bigskipamount
      \item Clear idea and message?
      \item Appropriate data?
      \item Documentation of sources?
      \item Effective graphics?
      \item Professional appearance?
\end{itemize}
\bigskip

\section*{Idea}

\vspace*{0.5in}

%\begin{itemize} \itemsep=2\bigskipamount
%\item Clarity of the message
%\item ..
%\end{itemize}


\section*{Data}

\vspace*{0.5in}

%\begin{itemize} \itemsep=2\bigskipamount
%\item Clarity of the message
%\item ..
%\end{itemize}

\section*{Model}

\vspace*{0.5in}


\section*{Graphics}

\vspace*{0.5in}

%\begin{itemize} \itemsep=2\bigskipamount
%\item Clarity of the message
%\item ..
%\end{itemize}

\section*{Difficulty}

\vspace*{0.5in}

%\begin{itemize} \itemsep=2\bigskipamount
%\item Clarity of the message
%\item ..
%\end{itemize}

\section*{Professional look}

\vspace*{0.5in}

%\begin{itemize} \itemsep=2\bigskipamount
%\item Clarity of the message
%\item ..
%\end{itemize}


\input{footer.tex}

\end{document}
